The CMS Data Aggregation System

### 2010-05-04 doc/das_paper/paper.tex
Added use case into Section 4
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@2081 4525493e-7705-40b1-a816-d608a930855b

\section{Data Aggregation System\label{DAS}}
The goal of the Data Aggregation System (DAS) was to fetch and aggregate meta-data 
on demand from existing CMS data-services under one umbrella by using their APIs, 
security policies, etc. In contrast, the approaches
discussed in \cite{DBXplorer, QueryAnswer, FedDB}
enforce a publication step of data into a dedicated database 
or central repository \cite{iRODS}. Therefore, quite often it was required
that data should be converted into common data structure/format in order to enable
aggregation, see \cite{OpenArchive}. In DAS the data are provided
by existing data-services and infrastructure, whose implementation,
data representation and security policies are left intact. Consequently,
DAS does not require a data preservation and transaction capabilities. 
Instead DAS can be treated as proxy or caching layer where information 
retrieval and aggregation are triggered dynamically by user queries. 
Below we discuss in details the DAS architecture.

@@

\section{Future work}
The DAS system was desgined for CMS HEP experiment, while its architecture is
transparent to consumed meta-data, data formats and participating data-providers. 
In the current year we plan to put DAS into production and confirm its scalability, 
transparency and durability for various CMS data-services. Our goal is to sustain 
in DAS 1TB of meta-data per year. The DISCOVER Research Service Group at Cornell 
University \cite{DRSG} is expressed its interests to apply DAS for other 
scientific domains and turn it into generic open-source project.

>>>>

\section{Data Aggregation System\label{DAS}}
The goal of the Data Aggregation System (DAS) was to fetch and aggregate meta-data 
on demand from existing CMS data-services under one umbrella by using their APIs, 
security policies, etc. In contrast, the approaches
discussed in \cite{DBXplorer, QueryAnswer, FedDB}
enforce a publication step of data into a dedicated database 
or central repository \cite{iRODS}. Therefore, quite often it was required
that data should be converted into common data structure/format in order to enable
aggregation, see \cite{OpenArchive}. In DAS the data are provided
by existing data-services and infrastructure, whose implementation,
data representation and security policies are left intact. Consequently,
DAS does not require a data preservation and transaction capabilities. 
Instead DAS can be treated as proxy or caching layer where information 
retrieval and aggregation are triggered dynamically by user queries. 
Imaging, a user opens a browser and places a query, e.g.
{\it file block=abc}. The DAS system responds with aggregated infromation about files
for provided set of conditions from all CMS data-services. Information
is either retrieved from the DAS cache or fetched on-demand from relevant
data-providers. Such system provides a uniform access to all meta-data in CMS 
via simple, intuitive query interface. It neither enforces users to learn 
the structure of CMS data-services
%, their intefaces, data-formats and access policies
or requires data-providers to agree on common data representation
and requirement to have central meta-data repository.

%Below we discuss in details the DAS architecture.

@@

\section{Future work}
In the near future we plan to put DAS into production and confirm its scalability, 
transparency and durability for various CMS data-services. 
Our interests are plug-able interface for participating data-providers;
analytics framework and pre-fetch strategies as well as horizontal scaling of the
system. Our goal is to sustain 1TB of meta-data per year. 
In a long term, we would like to use DAS across various
data-services in HEP community and other disciplines. Even though the DAS was developed
for CMS HEP experiment, its architecture is transparent to participating 
data-providers and meta-data content. Therefore the generalization of DAS is feasible.
Such work has began under the umbrella of DISCOVER Research Service Group at 
Cornell University \cite{DRSG} who expressed their interest to use DAS in other 
scientific domains.
